---
title: "Global Yield Gap Atlas"
subtitle: "Crop Management Data for CROP in COUNTRY"
output:
  pdf_document:
    latex_engine: xelatex
mainfont: Calibri
---

```{r, setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(magrittr)
```

This document is the companion document of the Global Yield Gap Atlas crop management form entitled: 
`GYGA_cropm_form_CROP_iso3.xlsx`. It includes a map of all the weather stations that will be used to perform yield gap estimation in COUNTRY for CROP as well as a table referencing all crop management parameters. The later table serves as a manual for `GYGA_cropm_form_CROP_iso3.xlsx`. It contains the name of all parameters, their detailed description and the format in which the data should be filled in. 

If you have any questions, please contact Antoine Langullaume (antoine.languillaume@wur.nl) or Joao Vasco Silva (joao.silva@wur.nl).

Thank you for involvement and the time you are dedicating to the Global Yield Gap Atlas.

The GYGA team.


```{r, fig.align = 'center'}
magick::image_read(here::here("./data/maps/country/wheat/map_CROP_iso3.png")) %>%
  magick::image_resize("75x75%")
```



```{r, message = FALSE}
d <- readr::read_csv(here::here("./data/crop-management/raw-forms/template/cropm_manual.csv"))
d %>%
  knitr::kable(format = "latex", booktabs = TRUE) %>%
  kableExtra::column_spec(2:3, width = "5cm") %>%
  kableExtra::row_spec(1:(nrow(d)-1), hline_after = TRUE) %>%
  kableExtra::row_spec(0, bold = TRUE)
```
